Responses to reviewers' comments and list of modifications done\\ on paper SORO226\\ \LARGE{\textbf{Grounding the interaction: anchoring situated discourse in everyday human-robot interaction}}

### 2011-07-16 cover_letter.tex
Added SORO num + typo

\title{Responses to reviewers' comments and list of modifications done\\ on paper !!!!!SOROXX paper ID!!!!!\\
\LARGE{\textbf{Grounding the interaction: anchoring situated discourse in everyday human-robot interaction}}}
\author{S\'everin Lemaignan \and Raquel Ros \and E. Akin Sisbot \and Rachid Alami \and Michael Beetz}

@@

At recent video showing the current state of the interaction can be viewed
here: \url{http://www.youtube.com/watch?v=IODx50uV_k4}

@@

I very strongly recommend that section I.A. be completely revised.

>>>>

\title{Responses to reviewers' comments and list of modifications done\\ on paper SORO226\\
\LARGE{\textbf{Grounding the interaction: anchoring situated discourse in everyday human-robot interaction}}}
\author{S\'everin Lemaignan \and Raquel Ros \and E. Akin Sisbot \and Rachid Alami \and Michael Beetz}

@@

A recent video showing the current state of the interaction can be viewed
here: \url{http://www.youtube.com/watch?v=IODx50uV_k4}

@@
